\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{0.5in}
\addtolength{\textheight}{1in}
\addtolength{\voffset}{-1in}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large{Mikhail Solodovnikov}} & \textbf{June 2026}\\
   Email: \href{mailto:miksolodovnikov@gmail.com}{miksolodovnikov@gmail.com}\\
%   LinkedIn \\
   LinkedIn: \href{https://www.linkedin.com/in/mikhsol}{mikhsol}\\

%   GitHub \\
   GitHub: \href{https://github.com/mikhsol}{mikhsol}\\
 \end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Perm State University}{Perm, Russia}
      {}{Not completed, Sep. 2013 -- Jun. 2015}
      {Master of Science in Finance and Information Technology. \\ Researched financial-market bubbles using LPPL models \\and studied systemic risks in the European banking system. CFA Institute Research Challenge 2014 participant.}
    \resumeSubheading
      {Perm State University}{Perm, Russia}
      {}{Graduated in Jul. 2012}
      {Specialized in Computational Fluid Dynamics. \\ Researched convection of liquid ternary mixtures in connected channels.}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
  \resumeSubheading
      {\href{https://microsoft.com/}{Microsoft}}{Dublin}
      {Senior Software Development Engineer, OMEX}{April 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Software Engineering}{
          \begin{itemize}
            \item Architected and launched a secure CI/CD pipeline for Word Web components, embedding compliance gates and eliminating manual release steps to accelerate delivery cadence.
            \item Built telemetry and dashboards for binary-size and performance guardrails, enabling proactive regression detection across every pipeline stage.
            \item Led the DWriteCore code/data-reduction effort, shrinking the text-rendering binary by 17\% and directly improving cold-boot KPIs.
            \item Designed and analyzed iterative A/B experiments that quantified boot-performance trade-offs of new components, informing investment decisions with session-mix insights.
            \item Prototyped and implemented server-side rendering for Word Web, collaborating with infrastructure team to target a more than 50\% boot-time reduction.
          \end{itemize}
        }
        \resumeItem{Operations}
                    {Own production support for Word Web, triage incidents end-to-end, and drive reliability/root-cause remediations across service teams.}
        \resumeItem{Collaboration} {
          \begin{itemize}
            \item Surface team-level productivity blockers and craft learning plans to amplify execution capacity.
            \item Facilitate cross-org syncs to align roadmaps, codify shared practices, and remove dependencies that slow delivery.
          \end{itemize}
        }
    \resumeItemListEnd

   \resumeSubheading
      {\href{https://microsoft.com/}{Microsoft}}{Dublin}
      {Senior Software Development Engineer, Identity}{June 2022 -- April 2024}
      \resumeItemListStart
        \resumeItem{Software Engineering}
                   {Designed and developed data pipelines and built telemetry aggregations for partner teams' business-unit analytics. Applied best practices and improved processes.}
        \resumeItem{Operations}
                   {Provided 24/7 on-call support for a data-processing system. Supported partner teams with available telemetry. Addressed legacy gaps and improved system observability.}
    \resumeItemListEnd

   \resumeSubheading
      {\href{https://aws.amazon.com/}{Amazon}}{Dublin}
      {Software Development Engineer, AWS SES}{June 2019 -- June 2022}
      \resumeItemListStart
        \resumeItem{Software Engineering}
                   {Designed and developed highly scalable distributed software systems. Implemented software-delivery best practices and improved processes.}
        \resumeItem{Operations}
                   {Supported high system availability and SLA compliance. Mitigated system-wide, high-impact issues.}
        \resumeItem{AWS Security Guardian}
                   {Helped the service team maintain a high application-security bar.}
    \resumeItemListEnd
  
   \resumeSubheading
      {\href{https://tencoins.org}{Tencoins}}{Malta}
      {Software Engineer}{June 2018 -- Jan. 2019}
      \resumeItemListStart
        \resumeItem{Software Engineering}
          {Designed and developed the core of a cryptocurrency exchange service with a microservice architecture. Created cryptocurrency wallets for Bitcoin, Ethereum, and Tether (Omni layer).}
    \resumeItemListEnd

    \resumeSubheading
      {Consulting, Self Employed}{}
      {IT Consultant}{Sep. 2016 -- June 2019}
      \resumeItemListStart
        \resumeItem{Consulting in IT}
          {Researched project domains. Built web services with Django/Django REST, Postgres, AngularJS/ReactJS, and mobile apps with Ionic.}
    \resumeItemListEnd

    \resumeSubheading
      {Votetour}{}
      {CTO}{Mar. 2017 -- Sep. 2017}
      \resumeItemListStart
        \resumeItem{Management}
          {Arranged software-engineering workflows with continuous integration and test-driven development practices.}
        \resumeItem{Business Development}
          {Built B2B relationships between airlines and Votetour.}
        \resumeItem{Software Engineering}
          {Led requirements analysis, architecture, design, and development of a cloud-based platform for tourist collaboration, planning, and booking charter flights worldwide; the platform enabled partner airlines to arrange charter flights for tourist groups.}
    \resumeItemListEnd

    \resumeSubheading
      {\href{http://nebulytics.com}{Nebulytics}}{Moscow, Russia}
      {Software Engineer}{May 2015 -- Sep. 2016}
      \resumeItemListStart
        \resumeItem{Platform Development}
          {Participated in developing core features for a proprietary SaaS platform. Architected and developed server-side solutions using Java/Groovy/Grails/Python, client-side solutions using JavaScript/jQuery/Bootstrap, and database-side solutions using MariaDB/MySQL/Percona and a proprietary MySQL framework written with C++ macros in version one and Lisp in version two.}
        \resumeItem{Consulting}
          {Led requirements analysis, architecture, design, and development of solutions for company customers using the Nebulytics platform.}
        \resumeItem{DevOps}
          {Tuned load balancers. Configured the Elasticsearch/Logstash/Kibana stack for server performance monitoring. Worked on tools supporting the existing codebase (bash, Perl).}
      \resumeItemListEnd

    \resumeSubheading
      {JSC Prognoz, Center solutions for financial markets}{Perm, Russia}
      {Software Engineer}{Aug. 2014 -- May 2015}
      \resumeItemListStart
        \resumeItem{R\&D}
          {Researched fraudulent activity on the Moscow Stock Exchange. Developed models that helped the regulator (Bank of Russia) investigate money laundering, insider trading, and related cases.}
        \resumeItem{Software Development}
          {Integrated the created models into an existing stock-exchange monitoring application (Delphi/PL/SQL/Oracle Database). Developed a tool for connecting to the Moscow Stock Exchange and receiving transaction data using the FIX/FAST protocol (C++).}
      \resumeItemListEnd

    \resumeSubheading
      {JSC Prognoz, Direction of international development}{Perm, Russia}
      {QA Engineer}{May 2013 -- Aug. 2014}
      \resumeItemListStart
        \resumeItem{Quality Assurance}
          {Tested mobile, web, and desktop applications, application backends, and REST/SOAP services. Coordinated development teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Scientific Industrial Instrument Making Company, R\&D Department}{Perm, Russia}
      {Research Engineer}{Oct. 2011 -- May 2013}
      \resumeItemListStart
        \resumeItem{Measurement automation}
          {Created test stands for fiber lasers, fiber angular velocity sensors, and integrated optical modulators, enabling automated measurement of optical characteristics using devices such as optical spectrum analyzers, power meters, optical switches, and thermal boxes. Wrote PC-based control and report-generation software (LabView, C\#).}
        \resumeItem{R\&D}
          {Participated in applied research on fiber lasers as light sources for fiber-optic gyroscopes, metal markers, and fiber-optic amplifiers for telecom purposes. Researched their behavior across a wide range of temperature conditions and under vibration. \\
Conducted applied research on sensor behavior under temperature changes and theoretical studies of sensor noise using spectral methods.}
      \resumeItemListEnd

    \resumeSubheading
      {Perm State University}{Perm, Russia}
      {Physics Department Assistant}{Oct. 2011 -- Feb. 2012}
      \resumeItemListStart
        \resumeItem{Assistance}
          {Demonstrated physics experiments.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, Java}
      %\hfill
      \\
      \textbf{Technologies}{: Distributed Systems, Observability, Linux, CI/CD, TDD, Agile, Microservices, Blockchain, AWS, Performance}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
